Proofs as Programs in Classical Logic\\Notes

### 2021-11-08 Notes/notes.tex
added vampire example

>>>>

\begin{example}\hfill
	\begin{align*}
		1. &\forall x_0 : \text{Nat}(z + x_0 = x_0) & \text{Axiom}\\
		2.&\forall x_0x_1: \text{Nat}(s(x_0 + x_1) = s(x_0) + x_1) & \text{Axiom}\\
		3.&\neg\forall x_0 : \text{Nat}\exists x_1:\text{Nat}(x_1 + z = x_0) & \text{negated claim}\\
		4.&(\forall x_0:\text{Nat}\exists x_1:\text{Nat}, x_1 + z = x_0)\vee(\forall x_0:\text{Nat},z\neq x_0 + z)\vee&\\
		&\exists x_0:\text{Nat}(\forall x_1:\text{Nat}, x_1 + z\neq s(x_0)\wedge \exists x_1:\text{Nat}, x_1+z=x_0)&\text{Induction axiom (ENNF)}\\
		5.&\exists x_0: \text{Nat}\forall x_1: \text{Nat}(x_1 + z \neq x_0) & \text{ENNF transformation 3}\\
		6.&\forall x_1: \text{Nat}(x_1 + z \neq sk_0) & \text{skolemization 5}\\
		7.&(\forall x_0:\text{Nat}, sk_1(x_0) + z = x_0)\vee(\forall x_0:\text{Nat},z\neq x_0 + z)\vee&\\
		&(\forall x_1:\text{Nat}, x_1 + z\neq s(sk_2)\wedge sk_3+z=sk_2)&\text{skolemization 4}\\
		8.&x_1 + z\neq sk_0&\text{cnf 6}\\
		9.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee sk_2 = sk_3 + z&\text{cnf 7}\\
		10.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee x_2 + z\neq s(sk_2)&\text{cnf 7}\\
		11.&s(x_0 + x_1) = s(x_0) + x_1&\text{cnf 2}\\
		12.&z + x_0 = x_0&\text{cnf 1}\\
		13.&sk_1(x_0) + z = x_0\vee z\neq z\vee sk_2 = sk_3 + z&\text{superposition 9, 12}\\
		14.&sk_1(x_0) + z = x_0\vee sk_2 = sk_3 + z&\text{trivial inequality removal 13}\\
		15.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee s(x_3 + z)\neq s(sk_2)&\text{supserposition 10, 11}\\
		16.&sk_0\neq x_0\vee sk_2 = sk_3 + z&\text{superposition 8, 14}\\
		17.&sk_2 = sk_3 + z&\text{equality resolution 16}\\
		18.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee s(sk_2)\neq s(sk_2)&\text{superposition 15, 17}\\
		19.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z&\text{trivial inequality removal 18}\\
		20.&sk_1(x_0) + z = x_0\vee z\neq z&\text{superposition 12, 19}\\
		21.&sk_1(x_0) + z = x_0&\text{trivial inequality removal 20}\\
		22.&sk_0 \neq x_0&\text{superoisition 21, 8}\\
		23.&\bot&\text{equality resolution 22}
	\end{align*}
\end{example}

\begin{example}\hfill
	\begin{align*}
		1. &\vdash \lambda f. f(\lambda x.\text{id}_{x}): \text{Cont }\Pi_{x_0 : \text{Nat}}(z + x_0 = x_0) & \text{Axiom}\\
		2.&\vdash \lambda f. f(\lambda x_0x_1.\text{id}_{s(x_0 + x_1)}): \text{Cont }\Pi_{x_0:\text{Nat}}\Pi_{x_1: \text{Nat}}(s(x_0 + x_1) = s(x_0) + x_1) & \text{Axiom}\\
		3.&\vdash f: (\Pi_{x_0 : \text{Nat}}\Sigma_{x_1:\text{Nat}}x_1 + z = x_0)\to\bot & \text{negated claim}\\
		4.&\vdash \lambda f.:\text{Cont }(\Pi_{x_0 : \text{Nat}}\Sigma_{x_1:\text{Nat}}x_1 + z = x_0)\vee(\Pi_{x_0 : \text{Nat}}z\neq x_0 + z)\vee&\\
		&\Sigma_{x_0:\text{Nat}}(\Pi_{x_1:\text{Nat}}x_1 + z\neq s(x_0)\wedge \Sigma_{x_1:\text{Nat}} x_1+z=x_0)&\text{Induction axiom (ENNF)}\\
		5.&\exists x_0: \text{Nat}\forall x_1: \text{Nat}(x_1 + z \neq x_0) & \text{ENNF transformation 3}\\
		6.&\forall x_1: \text{Nat}(x_1 + z \neq sk_0) & \text{skolemization 5}\\
		7.&(\forall x_0:\text{Nat}, sk_1(x_0) + z = x_0)\vee(\forall x_0:\text{Nat},z\neq x_0 + z)\vee&\\
		&(\forall x_1:\text{Nat}, x_1 + z\neq s(sk_2)\wedge sk_3+z=sk_2)&\text{skolemization 4}\\
		8.&x_1 + z\neq sk_0&\text{cnf 6}\\
		9.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee sk_2 = sk_3 + z&\text{cnf 7}\\
		10.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee x_2 + z\neq s(sk_2)&\text{cnf 7}\\
		11.&s(x_0 + x_1) = s(x_0) + x_1&\text{cnf 2}\\
		12.&z + x_0 = x_0&\text{cnf 1}\\
		13.&sk_1(x_0) + z = x_0\vee z\neq z\vee sk_2 = sk_3 + z&\text{superposition 9, 12}\\
		14.&sk_1(x_0) + z = x_0\vee sk_2 = sk_3 + z&\text{trivial inequality removal 13}\\
		15.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee s(x_3 + z)\neq s(sk_2)&\text{supserposition 10, 11}\\
		16.&sk_0\neq x_0\vee sk_2 = sk_3 + z&\text{superposition 8, 14}\\
		17.&sk_2 = sk_3 + z&\text{equality resolution 16}\\
		18.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z\vee s(sk_2)\neq s(sk_2)&\text{superposition 15, 17}\\
		19.&sk_1(x_0) + z = x_0\vee z\neq x_1 + z&\text{trivial inequality removal 18}\\
		20.&sk_1(x_0) + z = x_0\vee z\neq z&\text{superposition 12, 19}\\
		21.&sk_1(x_0) + z = x_0&\text{trivial inequality removal 20}\\
		22.&sk_0 \neq x_0&\text{superoisition 21, 8}\\
		23.&\bot&\text{equality resolution 22}
	\end{align*}
\end{example}
